---
title: | 
  Morphological variations in a novel geographically-separated *Papilio*
  species from Maluku Utara province, Indonesia
authors: W. Zane Billings, Andreas Handel
bibliography: refs.bib
csl: aje.csl
format: docx
execute: 
  echo: false
---

```{r setup, include = FALSE}
library(gt)
```


# Abstract

You could put the abstract here, if you wanted to.

# Introduction

We studied some butterflies in Indonesia.

# Methods

We caught the butterflies and measured them. We used telepathy to figure out
the other things that we couldn't measure with a ruler. Three collectors
independently collected samples at each of three locations on daily hikes.

We used regression to do the statistics analysis [@gelman].

# Results

Demographic statistics are shown in [@tbl-table1]. We found that the
butterflies were different at each of the sites.

```{r}
#| label: tbl-table1
here::here("results", "t1.rds") |>
	readr::read_rds() |>
	gt::as_raw_html()
```


We also did some regressions, and those are in [@tbl-table2].

```{r}
#| label: tbl-table2
here::here("results", "t2.rds") |>
	readr::read_rds() |>
	gt::as_raw_html()
```


# Discussion

This paper is so good, it should be in Nature (Billings, personal communication, 2024).

# References
